Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
taking screenshots

Equipped with a two degree of freedom platform that houses a Microsoft Kinect, Golem Krang can
inspect and reason about its environment with visual data. In perceiving the environment, we propose
using a light-weight feasure-based recognition approach as opposed to full 3D based approaches that
use the entire mesh data such as the iterative closest point algorithm or over-segmentation methods.
Figure \ref{fig:detection} demonstrates a sample output of the framework.

@@

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/manipulation.png}
  \caption{.}
  \label{fig:manipulation}
\end{figure}

asdf

>>>>

Equipped with a two degree of freedom platform that houses a Microsoft Kinect, Golem Krang can
inspect and reason about its environment with visual data. In perceiving the environment, we propose
using a light-weight feasure-based recognition approach as opposed to full 3D based approaches that
use the entire mesh data such as the iterative closest point algorithm or over-segmentation methods.
Figure \ref{fig:detection} demonstrates a sample output of the framework.
% TODO Justify why not use planar segmentation and ICP

@@

The manipulation of multiple objects under motor and perception uncertainty requires a series of 
robust strategies both algorithmicly and in practical implementation. In this work, a wide range of
motion planning tools are adopted such as rapidly-expanding random trees (RRTs) \cite{kuffner2000rrt},
analytical inverse kinematics \cite{tolani2000real} and Jacobian control \cite{whitney1969resolved}. 
Additionally, to handle perception errors, we propose using guarded moves \cite{bejczy1977effect} 
that control the manipulator behavior until a predetermined tactile feedback is received. Moreover,
we deploy ``conformant motion'' behaviors where the robot action forces itself
and its environment to a desired state without any sensory feedback \cite{goldman1996expressive}.

\subsubsection{Motion planning}

Figure \ref{fig:manipulation} depicts the analytical inverse kinematics and the motion planning
steps during the manipulation of a cinder block to be used as a fulcrum. We use a predetermined
grasp location, the top surface with the holes at the sides (see Figure \ref{fig:manipulation}a).
Having observed the object and moved its base to a desirable configuration, the goal for Golem
Krang is to use one of its manipulators to grasp the object. To do so, we first use analytical
inverse kinematics to find configurations close to the object we can reach without collisions.
Figure \ref{fig:manipulation}a displays three configurations out of which the left most,
semi-transparent one collides with one of the wheels. Once a goal in arm jointspace is determined,
bidirectional RRTs with path shortening and smoothing are used to move the arm from its initial 
pose to the goal. Figure \ref{fig:manipulation}b demonstrates the keyframes as the left arm moves
around the cinder block to avoid collisions until it reaches the goal pose (green) in front of the grasp point.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/manipulation.png}
  \caption{Left: Candidate grasp poses for the block - left most in collision with wheel.
  Right: RRT trajectory to goal grasp pose, moving around the block to avoid collisions.}
  \label{fig:manipulation}
\end{figure}

\vspace{-2em}
\subsubsection{Guarded and conformant motions}

Once in position using motion planning, Golem Krang uses force/torque feedback at the end-effectors
to reach out to the cinder block until contact and ensure its grippers can grasp it. Such guarded
moves have proven to be simple, heuristic alternatives to visual servoing as the robot picks up
levers, and positions them on the fulcrum and inside the load.

In addition to guarded moves with sensory feedback, we also utilize conformant motions where
in order to localize the lever more precisely, the robot runs its wheels against the lever,
usually one of them first, turning its base flush against it and eliminating any visual positioning error.
Such motions have been used before to eliminate uncertainty in the initial configuration of manipulated
objects in assembly tasks by pushing the objects into known configurations. \cite{mason1986mechanics}

\section{Experiments}

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/asdf.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/asdfg.png}
  \caption{The mechanical advantage in forces}
  \label{fig:showOff}
\end{figure}

% The robot has to move its arms out of the way to visualize the objects.
